---
title: "Megan Fantes"
author: "Final Project"
date: "December 12, 2016"
output: html_document
runtime: shiny
---

To see my code, please visit [my github page](https://github.com/MeganFantes/FinalProject).

During my time in college, I have lived in two places: Boston, MA and Sydney, Australia. When I was living in Sydney, I could not help but compare and contrast the city Down Under with my home city of Boston. Our final project has given me the opportunity to further explore and formalize my observations comparing the two cities using my favorite tool: social media. My dream is to work in social media analytics, so using Twitter as the basis for our final project is basically my dream. Additionally, I *worked* in social media when I was in Sydney (I was a social media content and analysis intern at a social media agency), so my frame of reference for Sydney is already through the lens of social media.

# Data Collection

During the week of Monday, November 28 - Friday, December 2, I collected 7303 tweets in the city of Boston and 5948 tweets in the city of Sydney. I collected the tweets using the `streamR` package to access the Twitter API, and specifying the geographic coordinates of the two cities in the `filterstream` function. I defined Boston with the coordinate box:  

N: 42.40 E: -70.99 S: 42.23 W: -71.19  

and I defined Sydney with the coordinate box:  

N: -33.59 E: 151.35 S: -34.12 W: 150.52  

I determined these coordinates by going to Google Maps and typing in [Boston](https://www.google.com/maps/place/Boston,+MA/@42.3135421,-71.197244,11z/data=!3m1!4b1!4m5!3m4!1s0x89e3652d0d3d311b:0x787cbf240162e8a0!8m2!3d42.3600825!4d-71.0588801) and [Sydney](https://www.google.com/maps/place/Sydney+NSW,+Australia/@-33.8474026,150.6517651,10z/data=!3m1!4b1!4m5!3m4!1s0x6b129838f39a743f:0x3017d681632a850!8m2!3d-33.8688197!4d151.2092955), using the red boundary line that shows the outlines of the city to determine the farthest edges of the city, dropping a pin on the fathest edges, and finding the geographic coordinates of the pin.

# Mapping Tweets

Once I collected my tweets, I wanted to map them onto maps of the cities to see where exactly people were tweeting in the cities.

```{r, echo=FALSE,message=FALSE,warning=FALSE,results='hide', fig.show='hide'}
source(file = "mapping.R", echo = FALSE, print.eval = FALSE)
```

####**BOSTON:**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
boston.tweets.mapped
```

Tweets in Boston are most highly concetrated in the areas of the city known as Government Center and the Financial District. This is not surprising, as these two areas generally define the "downtown" area of Boston, i.e. where there is the highest concentration of people.

####**SYDNEY:**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sydney.tweets.mapped
```

Tweets in Sydney are most highly concentrated in the area of the city know as the Central Business District, or the CBD. This is the equivalent of "downtown" in Sydney, and it is where there is the highest concentration of people during the day. According to [Forbes](http://www.forbes.com/sites/bruceupbin/2012/05/09/when-to-make-stuff-go-viral-online/#6c59f6b52b50), the busiest times on Twitter are between 9am and 3pm on weekdays -- i.e. during business hours. In Sydney, no one acutally lives in the CBD, it is where the vast majority of the population works during the day. So it makes sense that tweets are highly concentrated in the CBD: if people tweet during the business day, and during the business day they are in the CBD, then people are tweeting from the CBD. As we move away from the CBD, the number of tweets decreases dramatically.

# Tweet Visualization

Once I knew *where* people were tweeting, I wanted know know *what* people were tweeting in each of these cities. I created a Shiny application to display wordclouds for the tweets in each city (*excluding hashtags*) and for the hashtags in each city.

```{r, echo=FALSE,message=FALSE,comment=FALSE,results='hide'}
# we will source the cleaning and analysis file here so we can access the clean_text function for the word clouds below
source("clean and analyze text.R")
```

```{r, echo=FALSE}
# BOSTON TWEETS
bostonText <- gsub("#\\w+ *", "", boston.text$text)
# SYDNEY TWEETS
sydneyText <- gsub("#\\w+ *", "", sydney.text$text)
# BOSTON HASHTAGS
boston.htags <- extract_hashtags(tweets.Boston$text)
# SYDNEY HASHTAGS
sydney.htags <- extract_hashtags(tweets.Sydney$text)

# The list of valid options for word cloud
categories <<- list("Boston Tweets" = "b.tweets",
                    "Boston Hashtags" = "b.hashtags",
                    "Sydney Tweets" = "s.tweets",
                    "Sydney Hashtags" = "s.hashtags")

shinyApp(ui = fluidPage(sidebarLayout(
                          # Sidebar with a slider and selection inputs
                          sidebarPanel(
                            selectInput("selection", "Choose a category:",
                                        choices = categories),
                            actionButton("update", "Change"),
                            hr(),
                            sliderInput("freq",
                                        "Minimum Frequency:",
                                        min = 1,  max = 50, value = 15),
                            sliderInput("max",
                                        "Maximum Number of Words:",
                                        min = 1,  max = 300,  value = 100)
                            ),
                          # show word cloud
                          mainPanel(plotOutput("plot"))
                          )
                        ),
         
         server = function(input, output, session) {
           # Define a reactive expression for the document term matrix
           terms <- reactive({
             # Change when the "update" button is pressed...
             input$update
             # ...but not for anything else
             isolate({
               withProgress({
                 setProgress(message = "Processing corpus...")
                 getWords(input$selection)
                 })
               })
             })
           # Make the wordcloud drawing predictable during a session
           wordcloud_rep <- repeatable(wordcloud)
           output$plot <- renderPlot({
             v <- terms()
             wordcloud_rep(v, scale=c(4,0.5), random.order=FALSE,
                           min.freq = input$freq, max.words=input$max,
                           colors=brewer.pal(8, "Dark2"))
           })
           },
         
         onStart = getWords <- memoise(function(category) {
             # Careful not to let just any name slip in here; a
             # malicious user could manipulate this value.
             if (!(category %in% categories))
               stop("Unknown category")
             text <- switch(category,
                            "b.tweets" = bostonText,
                            "b.hashtags" = boston.htags$hashtags,
                            "s.tweets" = sydneyText,
                            "s.hashtags" = sydney.htags$hashtags)
             text.corpus <- Corpus(VectorSource(text))
             text.corpus <- tm_map(text.corpus, content_transformer(PlainTextDocument))
             text.corpus <- tm_map(text.corpus, content_transformer(removeWords), c("amp", stopwords('english')))
             }
             ),
         
         options = list(width="100%", height=450)
         )
```

  Visualizing the tweets with these word clouds was far and away the most fascinating part of my exploration, because the wordclouds confirmed my my primary hypothesis about the culture in Boston vs. Sydney. When I was living in Sydney I was working at a startup company, so I got a sense of Sydney Work Culture. I have held many different jobs in Boston, so I also have a sense of the Boston Work Culture. When in Sydney, I noticed something about Boston that I had never truly considered before: Boston (and really the US as a whole) is **obsessed** with work. Sydney (and Australia as a whole), on the other hand, is more interested in developing a work-life balance.  
  
  We can see Boston's obsession with work in its hashtags wordcloud. The most popular hashtag in Boston is "#job", closely followed by "#hiring". In theory, social media is supposed to be a fun, social outlet for people to express themselves. Thus we would expect people to *not* talk about work on social media. But no, Boston is too obsessed with its work culture to ever stop thinking about jobs, careers, and working.  
  
  We can see Sydney's desire to *balance* work and life in its hashtag wordcloud. The most popular hashtag in Sydney is "#sydney" followed by hashtags like "#therocks", "#nowplaying", "#cubevenue", and "#gelatissimo". The Rocks is the primary area for Sydney's nightlife, so when someone says they are going to The Rocks, they mean they are going out to a bar or club with friends. #nowplaying and #cubevenue are hashtags used to indicate songs or artists that are being played on local radio stations or at local music venues. Gelatissimo is a popular gelato store chain in Sydney that nearly everyone frequents at least one per week. Sydney's hashtags quickly reveal it to be a city of people that like to have fun. They are proud of where they come from (#sydney), and they like to go out and live a full life (enjoying nightlife, music, and food).
  
# Comparative Text Analysis

To conclude my exploration of tweets in Boston vs. tweets in Sydney, I want to do a brief, simple text analysis. I want to see if there is a difference between the two cities in 4 areas:

1. Number of words per tweet  
2. Length of tweet (number of characters)  
3. Word length  
4. Number of hashtags per tweet  

With these four categories, I want to see if I can detect Australian slang. Aussies (the people of Australia) are notorious for their slang, their incessant shortening of words. One of my favorite moments from my time in Australia was a day when I was speaking to one of my coworkers and we talking about getting mosquito bites. During the disccussion I said the word "mosquito," and as soon as I said it my coworker stopped me and said in shock, "what did you just say?!" To which I tentatively replied, "mosquito?" And she exclaimed "It's a *mozzie*. Who can be *bothered* to say the word 'mosquito'?!" And it was on that day that I realized the intensity and sincerity of Australian slang.

We will start our analysis with descriptive statistics of each category from each city:

####**BOSTON:**

```{r, echo=FALSE}
renderTable(boston.descriptives, rownames = TRUE, colnames = TRUE)
```

####**SYDNEY:**

```{r, echo=FALSE}
renderTable(sydney.descriptives, rownames = TRUE, colnames = TRUE)
```

Great, we have some numbers...so what? How do we know that the two cities are different? We run t-tests!

We will run 4 t-tests, one test to compare each of the four qualities we have measured on the tweets in each city. In a t-test, we are comparing the means of two samples to see if they have equal means. For example, in the t-test for number of words per tweet, we will compare the number of words in every tweet in Boston to the number of words in every tweet in Sydney to see if the *average* number of words per tweet is *different* between the cities. If the means are different, then the p-value for the test will be < 0.05. Below is a table summarizing the results of the t-tests, listing the quality that was being tested, the p-value for the test, and the city that has the **larger** mean in that category.

```{r, echo=FALSE}
ttest1 <- t.test(b.num.words, s.num.words, conf.level = 0.95, alternative = "two.sided")
ttest2 <- t.test(b.tweet.length, s.tweet.length, conf.level = 0.95, alternative = "two.sided")
ttest3 <- t.test(b.word.length, s.word.length, conf.level = 0.95, alternative = "two.sided")
ttest4 <- t.test(b.num.hashtags, s.num.hashtags, conf.level = 0.95, alternative = "two.sided")

ttest.df <- data.frame("Quality" = c("Number of words", "Tweet length", "Word length", "Number of Hashtags"),
                       "p-value" = c(ttest1$p.value, ttest2$p.value, ttest3$p.value, ttest4$p.value),
                       "City with larger value" = c(ifelse(ttest1$estimate["mean of x"] > ttest1$estimate["mean of y"], "Boston", "Sydney"),
                                                    ifelse(ttest2$estimate["mean of x"] > ttest2$estimate["mean of y"], "Boston", "Sydney"),
                                                    ifelse(ttest3$estimate["mean of x"] > ttest3$estimate["mean of y"], "Boston", "Sydney"),
                                                    ifelse(ttest4$estimate["mean of x"] > ttest4$estimate["mean of y"], "Boston", "Sydney")))

renderTable(ttest.df, rownames = TRUE, colnames = TRUE)
```

According to the t-tests, the number of words, the length, and the number of hashtags are significantly different between the tweets of Boston and the tweets of Sydney (the p-values are so small that they are basically zero, which means that the difference is very significant). In all three cases, Boston has the higher count. People who are tweeting in Boston are sending longer tweets, tweets with more words, and tweets with more hashtags. It seems as if these tests prove my hypothesis about Aussie slang: Australians "can't be bothered" to say or write the whole word or phrase; they prefer shorter, more efficient communication.

However, the t-test for word lengths shows that there is NOT a significant difference in average word length of tweets in Boston vs. Sydney (the p-value is essentialy equal to 1, which is the highest it can be, indicating there is no difference at all between the two means). Finding that there is not a significant difference seems to directly *disprove* my hypothesis about Aussie slang. It seems as if our friends Down Under take just as much time as we do to type out full words -- or, alternatively, we are just as passionate about slang as the Aussies.

To see my code, please visit [my github page](https://github.com/MeganFantes/FinalProject).